---
title: "Case Study"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

### Load data
```{r}
data("nyc_airbnb")
str(nyc_airbnb)

## select a random set of rows in the dataframe
nyc_airbnb %>% 
  sample_n(1000)
```

### Brainstorming questions

* What is the best Airbnb in staten island for <$100?
* What price range is popular in each borough? Most rented?
* What apartment features are related to price?
* Cheapest room type in each neighborhood?
* Hosts have higher ratings?

* Average price of room type by borough

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(
    avg_price = mean(price, na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = room_type, y = avg_price, color = neighbourhood_group)) +
geom_point(aes(size = avg_price)) +
  labs(
    title = "Average Price of room type by Borough",
    x = "Room Type",
    y = "Average Price"
  )
```

* Price of airbnb by neighborhood
```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(price < 1000,
         neighbourhood_group == "Manhattan") %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```

Interactive visualization!!!
leaflet for mapping in r package
```{r}
#code didnt work 
#pal <- colorNumeric("viridis", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1)
```

